A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Add succinctness notice

In 1997, Andersen and Hulgaard~\cite{ANDERSEN97} proposeded extending OBDDs with
a third type of nodes representing \textit{operators}. The resulting
representation is referred to as \textit{Binary Expression Diagram}
(\textit{BED}). Such an operator node $n$ has one attribute $op(n)$, the binary
Boolean operator, and, like nonterminal nodes, two children $lo(n)$ and $hi(n)$.
Operator nodes represent their corresponding Boolean connectives in the BED graph.

Just like OBDDs, BEDs share equivalent Boolean subexpressions. Furthermore, BEDs
have their own set of manipulating operations, especially because of the operator
nodes. For example, the \textit{up-step} operation moves variables up in the BED
hierarchy, if possible. As an effect, operator nodes are pushed towards the
terminal nodes and some operator nodes may be evaluated if some of the associated
expressions are terminal nodes. The BED may be simplified afterwards. These steps
can be repeated to reduce the BED over and over again, and simplifying some tests,
e.g. tautology testing. It is also possible to move all variable up in a single
step. Nevertheless, reducing the BED step-by-step can exploit structural
information.

>>>>

In 1997, Andersen and Hulgaard~\cite{ANDERSEN97} proposeded extending OBDDs with
a third type of nodes representing \textit{operators}. The resulting
representation is referred to as \textit{Binary Expression Diagram}
(\textit{BED}). Such an operator node $n$ has one attribute $op(n)$, the binary
Boolean operator, and, like nonterminal nodes, two children $lo(n)$ and $hi(n)$.
Operator nodes represent their corresponding Boolean connectives in the BED
graph~\cite{ANDERSEN97}.

Just like OBDDs, BEDs share equivalent Boolean subexpressions. Furthermore, BEDs
have their own set of manipulating operations, especially because of the operator
nodes. For example, the \textit{up-step} operation moves variables up in the BED
hierarchy, if possible. As an effect, operator nodes are pushed towards the
terminal nodes and some operator nodes may be evaluated if some of the associated
expressions are terminal nodes. The BED may be simplified afterwards. These steps
can be repeated to reduce the BED over and over again, and simplifying some tests,
e.g. tautology testing. It is also possible to move all variable up in a single
step. Nevertheless, reducing the BED step-by-step can exploit structural
information~\cite{ANDERSEN97}.

In contrast to OBDDs, BEDs are \textit{exponentially more succinct} because
arbitrary circuits can be translated into BEDs. As a consequence, the BED
representation suffices to solve integer multiplication using a quadratic number
of nodes~\cite{ANDERSEN97}.
